### 2021-03-16 Figures/PPCA_Qualitative_Vars.Rmd
preparing all figures

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=13, fig.width=11}

@@

#Load libraries
#LOAD LIBRARIES
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours

@@

library(cowplot)
 plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC), ncol=2,nrow=3,  align = "v")

>>>>

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=17, fig.width=17}

@@

#Load libraries
#LOAD LIBRARIES
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours
library(cowplot)

@@

#############################################################################################################################################################
#Nectar
#############################################################################################################################################################
#Load plots
Nectar <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
  dat$Nectar[dat$Nectar=="no"] <- "Absence"
  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Nectar),size=1.5)+scale_color_manual(values=c("black","grey"))

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.095, 0.115)) + ggtitle("G)")

 #plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),Nectar(PC), ncol=2,nrow=4,  align = "hv")

  plot_grid(Compatibility(PC),Life_form(PC),Life_span(PC),Breeding_syst(PC),Flower_sha(PC),Flower_sym(PC),NULL,Nectar(PC),NULL, ncol=3,nrow=3,  align = "hv")

### 2021-03-16 Scripts/4_1_Visualize_Plant_Functional_Groups/7_plots.Rmd
preparing all figures

---
title: "Untitled"
output: pdf_document
---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=6}
setwd("~/R_Projects/Reproductive Traits")
library(dplyr)
library(ggplot2)
library(viridis)
library(grid)
library(cowplot)
library(gridExtra)

@@

library(cowplot)
 #Plant height
 p1 <- ggplot(t, aes(x = Clusters, y = log(IMPUTED_plant_height_mean_m)))+ geom_violin(aes(color = Clusters, fill = Clusters), 
 binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Plant height)")+geom_boxplot(width=0.1)+
 theme(legend.position = "none")
 #Flower size
 p2 <- ggplot(t, aes(x = Clusters, y = log(Floral_unit_width)))+ geom_violin(aes(color = Clusters, fill = Clusters), 
 binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Flower size)")+geom_boxplot(width=0.1)+
 theme(legend.position = "none")
 #Ovule number
 p3 <- ggplot(t, aes(x = Clusters, y = log(OVULES_IMPUTED)))+ geom_violin(aes(color = Clusters, fill = Clusters), 
 binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Ovules per flower)")+geom_boxplot(width=0.1)+
 theme(legend.position = "none")
 #Style length
 p4 <- ggplot(t, aes(x = Clusters, y = log(STYLE_IMPUTED)))+ geom_violin(aes(color = Clusters, fill = Clusters), 
 binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Style length)")+geom_boxplot(width=0.1)+
 theme(legend.position = "none")
 #Flowers per plant
 p5 <- ggplot(t, aes(x = Clusters, y = log(Flowers_per_plant)))+ geom_violin(aes(color = Clusters, fill = Clusters), 
 binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Flowers per plant)")+geom_boxplot(width=0.1)+
 theme(legend.position = "none")
 #Flowers per plant
 p6 <- ggplot(t, aes(x = Clusters, y = Autonomous_selfing_level_fruit_set))+ geom_violin(aes(color = Clusters, fill = Clusters), 
 binaxis='y', stackdir='center')  +theme_classic()+ ylab("log(Selfing)")+geom_boxplot(width=0.1)+
 theme(legend.position = "none")

#Load libraries
#LOAD LIBRARIES
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours

# Theme for publication
theme_ms <- function(base_size=12, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
      theme(text=element_text(color="black"),
            axis.title=element_text( size = rel(1.3)),
            axis.text=element_text(size = rel(2), color = "black"),
            legend.title=element_text(face="bold"),
            legend.text=element_text(),
            legend.background=element_rect(fill="transparent"),
            legend.key.size = unit(0.9, 'lines'),
            panel.border=element_rect(color="black",size=1),
            panel.grid.minor.x =element_blank(),
            panel.grid.minor.y= element_blank(),
             panel.grid.major= element_blank()
      ))
}

#Load data
dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca.rds")
phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")

PC <- phyl_pca_forest
#CHECK CONTENT
#EIGENVALUES
PC$Eval
#PC score (POINTS)
PC$S
#PC loadings (ARROWS)
PC$L

#############################################################################################################################################################
#COMPATIBILITY
#############################################################################################################################################################
#Load plots
all_spp <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

@@

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$Clusters <- dat_cleaning_5$Clusters
 dat$Clusters <- as.factor(dat_cleaning_5$Clusters)
  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Clusters),size=2)+ scale_color_manual(values =  c("#00AFBB", "#E69F00", "#FC4E07","#000000", "#009E73"))

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .75 * mult * (get(x)),
                      v2 = .75 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="black")

@@

 # plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),")","%", sep = "")) #XLAB
  #plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
  #plot <- plot + theme(panel.grid.minor = element_blank(),panel.grid.major = element_blank(),
   #                    panel.border = element_rect(linetype = "solid", colour = "black", size=1))

  #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower N.", "Flower size", "Style Length", "Ovule N.", "Plant Height" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.35,5,7.5,7.1,6)), y = -(PCAloadings$PC2*c(4.3,5,5,7,5.8,6.5)),
                          label = PCAloadings$Variables, color="black",size=5)

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.07, 0.11)) +ggtitle("") +xlab("")+ylab("")

@@

p1 <- plot_grid(all_spp(PC))

#p3 <- PCbiplot(PC)

p2 <- plot_grid(breeding,Compatibility,Flower_morphology,Flower_symmetry,life_form,lifespan,
        nrow = 3,ncol=2,align = 'h')

plot_grid(p1,p2,ncol=1)

#top <- plot_grid(p1,p2,p3,p4,p5,p6, nrow = 2,ncol=3,align = 'v')

#plot_grid(top,bottom,nrow = 2)

>>>>

---
title: ""
output: pdf_document
---

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=6, fig.width=15}
setwd("~/R_Projects/Reproductive Traits")
library(dplyr)
library(ggplot2)
library(viridis)
library(grid)
library(cowplot)
library(gridExtra)

@@

#######################################################################################################################################
 plot_grid(breeding,Compatibility,Selfing,Flower_morphology,Flower_symmetry,life_form,lifespan, nrow = 2,ncol=3,align = 'v')

phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")
dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca.rds")

#CALL the output PC for simplicity
PC <- phyl_pca_forest
#CHECK CONTENT
#EIGENVALUES
PC$Eval
#PC score (POINTS)
PC$S
#PC loadings (ARROWS)
PC$L

PCbiplot <- function(PC, x="PC1", y="PC2") {
  # PC being a prcomp object
  data <- data.frame(PC$S)
  plot <- ggplot(data, aes_string(x=x, y=y)) #generate plot
  dat <- data.frame(x = data[,x], y = data[,y])

@@

  dat$density <- get_density(dat$x, dat$y, h = c(2, 2), n = 1000) #obtain density
  dat$Clusters <- dat_cleaning_5$Clusters
  dat$Clusters <- as.factor(dat$Clusters)
  plot <- plot + geom_point(data=dat, aes(-x, -y, colour=Clusters),size=1.5)+scale_color_manual(values=c("blue", "purple","green","orange","red")) #+ #scale_color_viridis_c(option = "A", direction = 1, limits = c(min(dat$density), max(dat$density)))+
  # plot <- plot +geom_point(data=dat, aes(-x, -y, colour = density),size=0.65,shape = 1,colour = "black",alpha=0.8)

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .5 * mult * (get(x)),
                      v2 = .5 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=-v2),size=1, arrow=arrow(length=unit(0.5,"cm")), alpha=1, color="brown4")

  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),")","%", sep = "")) #XLAB
  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB
  plot <- plot + theme(panel.grid.minor = element_blank(),panel.grid.major = element_blank(),
                       panel.border = element_rect(linetype = "solid", colour = "black", size=1))

@@

  #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower Number", "Flower size", "Style Length", "Ovule Number", "Plant Height" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(3.5,4,4,4,4,4)), y = -(PCAloadings$PC2*c(3,4,4,4,4,4)),
                          label = PCAloadings$Variables, color="black",size=5)

@@

  plot <- plot + theme_bw()

  #CALCULATE KERNELS
  #mv.kde <- kde2d(data[,1], data[,2], n = 400)
  #dx <- diff(mv.kde$x[1:2])  # lifted from emdbook::HPDregionplot()
  #dy <- diff(mv.kde$y[1:2])
  #sz <- sort(mv.kde$z)
  #c1 <- cumsum(sz) * dx * dy

  # specify desired contour levels:
  #prob <- c(0.5)
  #prob_1 <- c(0.90)
  # plot:
  #dimnames(mv.kde$z) <- list(mv.kde$x,mv.kde$y)
  #dc <- melt(mv.kde$z)

  #dc$prob <- approx(sz,1-c1,dc$value)$y

  #plot <- plot + geom_contour(data=dc, aes(x=-Var1,y=-Var2,z=prob),colour="brown4",breaks=prob)
  # plot:
  #dimnames(mv.kde$z) <- list(mv.kde$x,mv.kde$y)
  #dc <- melt(mv.kde$z)

  #dc$prob_1 <- approx(sz,1-c1,dc$value)$y
  #plot <- plot + geom_contour(data=dc, aes(x=-Var1,y=-Var2,z=prob_1),colour="black",breaks=prob_1)

@@

p3 <- PCbiplot(PC)

library(patchwork)

p3 / (breeding | Compatibility)
